HO unification from object language to meta language

### 2024-04-03 paper/main.tex
add some notes

\begin{lemma}
  Given a \linketa $l$, the unification done by \progressetaleft is between
  terms in $\wellb$  
  \label{lemma:unif-eta-1}
\end{lemma}

@@

@@

\noteE[inline]{IIRC, second order unification, where variables can stand for functions, is semi-decidable, indeed Huet's algorith enumerates all solutions. Third order, functions that take functions, is undecidable, proved by Dowek. IMO here the problem is that there is no unique solution, (semi)decidability is a secondary point. This paragraph needs fixing.}
Until now, we have only dealt we unification of terms in \llambda. However, we
want the unification relation to be more robust so that it can work with terms
in \maybebeta. In general, unification in \maybebeta admits more then one
solution and commiting one of them in the substitution does not guarantee
prop.~\ref{prop:complete}. For instance, $X \appsep a \Uo a$ is a unification
problem admits two different substitutions: $\rho_1 = \{X \mapsto \lambda x.x\}$
and $\rho_2 = \{X \mapsto \lambda \_.a\}$. Prefer one over the other may break
future unifications.

@@

In the example above, we see that $\foUnifPb_1$ instantiates $X$ so that
$\foUnifPb_2$, can be solved in \llambda.
\noteE[inline]{it is even a ground term, there is no unification left to perform actually}
On the other hand, we see that, 
\Ue can't solve the compiled problems \hoUnifPb. In
fact, the resolution of $\hoUnifPb_1$ gives the substitution $\sigma = \{ A
\mapsto \lambda x. B\}$, but the dereferencing of $\hoUnifPb_2$ gives the 
non-unifable problem $(\lambda x. B) \appsep a \Ue a$.

@@

\newcommand{\rhsBetaHead}{\ensuremath{X_{s_1\dots s_n}}}
\newcommand{\rhsBeta}{\ensuremath{\rhsBetaHead\appsep t_1\dots t_m}\xspace}
% \noteE[inline]{Io direi $X_{s_1\ldots s_n}\appsep l_1\ldots l_m$
% ... where S = [s1 .. sn] e L = [l1 .. lm]}
\noteE[inline]{Is it clearer?}

>>>>

\noteD[inline]{Below the proof of \cref{prop:nf}, ho usato 3 lemmi ausiliari,
forse si può compattare in una prova più piccola?}
\begin{lemma}
  Given a \linketa $l$, the unification done by \progressetaleft is between
  terms in $\wellb$  
  \label{lemma:unif-eta-1}
\end{lemma}

@@

\noteD[inline]{Should we proove simulation fidelity for \linketa insertion?}

@@

% \noteE[inline]{IIRC, second order unification, where variables can stand for functions, is semi-decidable, indeed Huet's algorith enumerates all solutions. Third order, functions that take functions, is undecidable, proved by Dowek. IMO here the problem is that there is no unique solution, (semi)decidability is a secondary point. This paragraph needs fixing.}
\noteD[inline]{I've rewritten it, it is clearer?}
Until now, we have only dealt we unification of terms in \llambda. However, we
want the unification relation to be more robust so that it can work with terms
in \maybebeta. In general, unification in \maybebeta admits more then one
solution and commiting one of them in the substitution does not guarantee
prop.~\ref{prop:complete}. For instance, $X \appsep a \Uo a$ is a unification
problem admits two different substitutions: $\rho_1 = \{X \mapsto \lambda x.x\}$
and $\rho_2 = \{X \mapsto \lambda \_.a\}$. Prefer one over the other may break
future unifications.

@@

In the example above, we see that $\foUnifPb_1$ instantiates $X$ so that
$\foUnifPb_2$, can be solved in \llambda.
\noteE[inline]{it is even a ground term, there is no unification left to perform actually}
\noteD[inline]{i don't understand the note}
On the other hand, we see that, 
\Ue can't solve the compiled problems \hoUnifPb. In
fact, the resolution of $\hoUnifPb_1$ gives the substitution $\sigma = \{ A
\mapsto \lambda x. B\}$, but the dereferencing of $\hoUnifPb_2$ gives the 
non-unifable problem $(\lambda x. B) \appsep a \Ue a$.

@@

\newcommand{\rhsBetaHead}{\ensuremath{X_{s_1\dots s_n}}}
\newcommand{\rhsBeta}{\ensuremath{\rhsBetaHead\appsep t_1\dots t_m}\xspace}
% \noteE[inline]{Io direi $X_{s_1\ldots s_n}\appsep l_1\ldots l_m$
% ... where S = [s1 .. sn] e L = [l1 .. lm]}
\noteD[inline]{Is it clearer?}
